\documentclass[10pt,a4paper,ragged2e]{altacv}
\geometry{left=2cm,right=10cm,marginparwidth=6.8cm,marginparsep=1.2cm,top=1.25cm,bottom=1.25cm}
\ifxetexorluatex
  \setmainfont{Carlito}
\else
  \usepackage[utf8]{inputenc}
  \usepackage[T1]{fontenc}
  \usepackage[default]{lato}
  \usepackage{hyperref}
  \usepackage{longfbox}
\fi
\definecolor{VividPurple}{HTML}{000000}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{2E2E2E}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}
\addbibresource{sample.bib}

\begin{document}
\name{Dylan Cancelliere}
\tagline{Rochester Institute of Technology}
\personalinfo{
  \href{mailto:dycancel@gmail.com}{\faEnvelopeO \space dycancel@gmail.com} \quad \quad
  \phone{203-214-5684}
  \href{https://www.linkedin.com/in/dylan-cancelliere/}{\linkedin{linkedin.com/in/dylan-cancelliere}}
  \href{https://github.com/dylan-cancelliere}{\faicon{github}{ github.com/dylan-cancelliere}}
}

\begin{fullwidth}
\makecvheader
\end{fullwidth}

\AtBeginEnvironment{itemize}{\small}

\cvsection[page1sidebar]{Work Experience}

\cvevent{\href{https://www.hubspot.com/}{HubSpot} | \emph{Fullstack Software Engineer Intern}}{}{Jan 2021 -- Aug 2021}{Remote}
\begin{itemize}
\item Redesigned cookie banner settings page and implemented auto-saving feature.
\smallskip
\item Created UX to display cookie scan reports and built a report generator to summarise new scans and email results.
\smallskip
\item Implemented Kafka-like message queuing system to flatten load on heavily used endpoints.
\end{itemize}

\divider

\cvevent{\href{https://www.constantcontact.com/}{Constant Contact} | \emph{Software Engineer Intern}}{}{Jun 2020 - Aug 2020}{Remote}
\begin{itemize}
\item Built a standard feature gating process for beta features and internal adopters.
\smallskip
\item Helped identify and resolve bugs ahead of release of mobile app to over 600,000 customers.
\smallskip
\item Engineered various frontend changes on the flagship cross platform email editor.
\end{itemize}

\cvsection[]{Projects}

\cvevent{AutoRecipe | \emph{React, Redux, NodeJS}}{\underline{\href{https://github.com/dylan-cancelliere/auto-recipe}{\faicon{github} https://github.com/dylan-cancelliere/auto-recipe}}}{}{}
\begin{itemize}
\item App to suggest recipes based on what's already in your house.
\smallbreak
\item Built a web scraper to build a database of ingredients and recipes from \href{https://tasty.co/}{\underline{tasty.co}}.
\smallskip
\item Stores user session and ingredients that a user has added to their virtual pantry.
\end{itemize}

\divider

\cvevent{AutoDJ | \emph{React, NodeJS}}{\underline{\href{https://github.com/dylan-cancelliere/auto-dj}{\faicon{github} https://github.com/dylan-cancelliere/auto-dj}}}{}{}
\begin{itemize}
    \item Crowdsources music selection by adding tracks to a queue and having users vote on which songs they want to hear.
    \smallskip
    \item Uses \underline{\href{https://developer.spotify.com/documentation/web-api/}{Spotify Web API}} for music selection and playback.
    \smallbreak
    \item Conforms to OAuth2 flow for user authentication.
\end{itemize}

\divider

\cvevent{Morning Announcements App | \emph{Java}}{\underline{\href{https://github.com/dylan-cancelliere/announcements}{\faicon{github} https://github.com/dylan-cancelliere/announcements}}}{}{}
\begin{itemize}
    \item App to keep track of announcements and upcoming events from my high school.
    \smallskip
    \item Pulls data from simple Google Sheets "database" from the \underline{\href{https://developers.google.com/sheets/api}{Sheets API}}.
    \smallskip
    \item Self taught Android Studio and app design principles alongside learning Java in class.
\end{itemize}

\clearpage
\end{document}
